Flowchart of Current Algorithm

### 2009-02-03 docs/flowchart/flowchart.tex
more Initialization cleanup

\section{Time Advancement Algorithm}

@@

The initial perturbational pressure also needs to be determined for
use in steps 2, 7 and 11. 
This is done through a second iterative procedure which follows the
time advancement algorithm as described in steps 1-11 in \S~ref{Sec:Alg}.  
The user specifies the number of iterations, 
$N_{\rm iters}^{\pi},$ in this second step of the initialization procedure.
The details for both iterations are given below.\\

@@

Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ an 
initial base state, and an initial guess for the velocity, $\Ub^{\initp}.$
Use the equation of state to determine $(\rho h)^{\initp}$.  Set
$w_0^0 = 0$ as an initial approximation.  Compute $\beta_0^{\initp}$ as a function of 
the initial data.  Then, project $\Ub^{\initp}$ using $\beta_0^{\initp}$ and 
$S = \rho\Hext$, giving $\Ub^{0,0}$.  The next part of the initialization process 
proceeds as follows.

@@

Next, we need to construct an approximation to the time-centered perturbational pressure,
$\pi,$  and an approximation to the divergence constraint at the end of the
first time step.  As initial approximations, set $\etarho^{-\myhalf}=0$, $\psi^{-\myhalf}=0$,
$S^{1,0}=S^0$, and $\pi^{-\myhalf}=0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}

>>>>

\section{Time Advancement Algorithm}\label{Sec:Time Advancement Algorithm}

@@

The initial perturbational pressure also needs to be determined for
use in steps 2, 7 and 11. 
This is done through a second iterative procedure which follows the
time advancement algorithm as described in steps 1-11 in 
\S~\ref{Sec:Time Advancement Algorithm}.  
The user specifies the number of iterations, 
$N_{\rm iters}^{\pi},$ in this second step of the initialization procedure.
The details for both iterations are given below.\\

@@

First, we need to construct approximations to $S^0, w_0^{-\myhalf}, \Delta t^0$, 
and $\Ub^0$.  Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ an 
initial base state, and an initial guess for the velocity, $\Ub^{\initp}$.
Set $w_0^0 = 0$ as an initial approximation.  Use the equation of state to 
determine $(\rho h)^{\initp}$.  Compute $\beta_0^{\initp}$ as a function of 
the initial data.  Then, project $\Ub^{\initp}$ using $\beta_0^{\initp}$ and 
$S = \rho\Hext$, giving $\Ub^{0,0}$.  The next part of the initialization process 
proceeds as follows.

@@

Next, we need to construct approximations to $\etarho^{-\myhalf}, \psi^{-\myhalf}, S^1$,
and $\pi^{-\myhalf}$.  As initial approximations, set 
$\etarho^{-\myhalf}=0, \psi^{-\myhalf}=0, S^{1,0}=S^0$, and $\pi^{-\myhalf}=0.$
\begin{enumerate}
  \renewcommand{\theenumi}{{\bf \alph{enumi}}}
  \renewcommand{\labelenumii}{\roman{enumii}.}
  \addtocounter{enumi}{1}
